---
title: "PM579-final-project-multiple-testing"
author: "Camellia Rui"
date: "7/30/2021"
output: html_document
---
## Install packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("readxl")
if(!require("genefilter")) {BiocManager::install("genefilter")}
library(readxl)
library(tidyverse)
library(genefilter)
library(limma)

```

## Read in data
```{r ReadData}
csfdata <- read_excel('data/csf_reform.xlsx')
plasmadata <- read_excel('data/plasma_reform.xlsx')
head(csfdata)
```
csf is all the measurements within cerebrospinal fluid, plasma is all the measurements within plasma. 

# Check missing data
```{r missing}
is.na(csfdata)

```
# Calculate descriptive statistics
```{r descriptive}


```
# Multiple testing for before/after treatment
for csf group: H0: the mean difference of fatty acids measured in csf is the same from the same patient before and after the treatment
H1: the mean difference of fatty acids measured in csf is the different from the same pateint before and after the treatment

for plasma group: the mean difference of fatty acids measured in plasma is the same from the same patient before and after the treatment
H1: the mean difference of fatty acids measured in plasma is the different from the same pateint before and after the treatment

```{r multiple testing for csf data}
library(genefilter)
group = factor(rep(c("A","B"), c(126,126)))
res = rowttests(as.matrix(csfdata),factor(group))
res$adjP = p.adjust(res$p.value, "BH")
head(res)
               
```
```{r histogram}
hist(res$p.value)
```
```{r multiple testing for plasma data}
library(genefilter)
group = factor(rep(c("A","B"), c(126,126)))
res = rowttests(as.matrix(plasmadata),factor(group))
res$adjP = p.adjust(res$p.value, "BH")
head(res)
               
```

```{r histogram for plasma data}
hist(res$p.value)
```
